Adopting agile in the large: motivations, success factors and challenges

### 2013-01-26 tex/article.tex
Motivation: encourage large organizations to adopt agile

The goal of this research is to explore how and why large organizations adopt
agile methods. Studies on large scale agile transformations have been published,
but no extensive or summarizing research is available on the subject. In this
paper we will give an overview of reported case studies on adopting agile
methods in large organizations. We will further discuss the motivations for
adopting agile methods, the characteristics of agile transformations, and
factors relating to success or challenge in the transformation process. Our
research is focused on the process of organizational change. We leave out topics
related to comparing the initial and transformed states of organizations, such
as measuring the performance of organizations before and after the
transformation.

@@

Introducing agile methods in large organizations is more difficult than it is in
small organizations \citegen{Dyba2008}. The difficulty is partly related to size
bringing higher organizational inertia which slows down organizational change
\citegen{Livermore2008}. Agile methods are not founded on the use of individual
tools or practices, but rather on a holistic way of thinking.
Adopting agile often requires change of the entire organizational culture
\citegen{Misra2010}.

One significant difference between small and large scale adoptions is that large
organizations have more dependencies between projects and teams. This increases
the need for formal documentation and thus reduces agility \citegen{Lindvall2004}.
In addition to inter-team coordination development teams are required to
interact with other organizational units, which are often non-agile in
nature. For instance, HR may demand individuals to have strictly specified roles
in projects \citegen{Boehm2005}, or a change control board may inhibit the use of
continuous integration or refactoring \citegen{Lindvall2004}. All units affected
by the agile transformation need to be informed and consulted, and the agile
process must be adjusted according to their needs \citegen{Lindvall2004,
Cohn2003, Boehm2005}.

>>>>

The goal of this research is to explore how and why large organizations adopt
agile methods. Studies on large scale agile transformations have been published,
but no extensive or summarizing research is available on the subject.
By this literature review we hope to provide evidence that encourages large
organizations to consider adopting agile methods.
In this paper we will give an overview of reported case studies on adopting
agile methods in large organizations. We will further discuss motivations
for adopting agile methods, characteristics of agile transformations, and
factors relating to success or challenge in the transformation process. Our
research is focused on the process of organizational change. We leave out topics
related to comparing initial and transformed states of organizations, such
as measuring performance before and after the transformation.

@@

Introducing agile methods in large organizations is more difficult than it is in
small organizations \citegen{Dyba2008}. The difficulty is partly related to size
bringing higher organizational inertia which slows down organizational change
\citegen{Livermore2008}. Agile development is not founded on the use of individual
tools or practices, but rather on a holistic way of thinking.
Adopting agile often requires change of the entire organizational culture
\citegen{Misra2010}.

One significant difference between small and large scale adoptions is that large
organizations have more dependencies between projects and teams. This increases
the need for formal documentation and thus reduces agility \citegen{Lindvall2004}.
In addition to inter-team coordination development teams must
interact with other organizational units, which are often non-agile in
nature. For instance, HR may demand individuals to have strictly specified roles
in projects \citegen{Boehm2005}, or a change control board may inhibit the use of
continuous integration or refactoring \citegen{Lindvall2004}. All units affected
by the agile transformation need to be informed and consulted, and the agile
process must be adjusted according to their needs \citegen{Lindvall2004,
Cohn2003, Boehm2005}.
